### 2020-03-22 CalNotes.tex
Two typos
update delta=epsilon^zeta

\corr{ CASE $\delta = \epl^\zeta$ (PROOF IN APPENDIX \ref{ap:zeta}).
\begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:convMeasure} hold, let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and let $\delta = \epl^\zeta$ with $\zeta \in (0,1)$. If $\widetilde M$ is invertible, then
		\begin{equation}
		\lim_{\epl \to 0} \lim_{T \to \infty} \widehat A_k^\epl(T) = A, \quad \text{in law},
		\end{equation}
		where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_MS}.
\end{theorem}}

@@

\begin{lemma}\label{lem:FilterJensen} Let $\delta > 0$ and $k(r)$ be defined as
	\begin{equation}
		k(r) = \frac1\delta e^{-r/\delta}.
	\end{equation}
	Then, for any $t > 0$, $p \geq 0$ and any function $g\in \mathcal C^0(0, t)$ it holds 
	\begin{equation}
		\abs{\int_0^t k(t-s) g(s) \dd s}^p \leq (1 - e^{-t/\delta})^{p-1}\int_0^t k(t-s) \abs{g(s)}^p \dd s.
	\end{equation}
	Moreover, if $p \geq 1$ and since $0 < (1-e^{-t/\delta}) < 1$ for all $t > 0$, it holds
	\begin{equation}
		\abs{\int_0^t k(t-s) g(s) \dd s}^p \leq \int_0^t k(t-s) \abs{g(s)}^p \dd s.
	\end{equation}
\end{lemma}
\begin{proof} Let us first note that
	\begin{equation}
		\int_0^t k(t-s) \dd s = 1 - e^{-t/\delta}.
	\end{equation}
	Therefore, the measure $\kappa_t(\d s)$ on $(0, t)$ defined as
	\begin{equation}
		\kappa_t(\d s) \defeq \frac{k(t-s)}{1 - e^{-t/\delta}} \dd s,
	\end{equation}
	is a probability measure. An application of Jensen's inequality therefore yields
	\begin{equation}
	\begin{aligned}
		\abs{\int_0^t k(t-s) g(s) \dd s}^p &\leq (1 - e^{-t/\delta})^p \int_0^t \abs{g(s)}^p \kappa_t(\d s) \\
		&= (1 - e^{-t/\delta})^{p-1} \int_0^t k(t-s) \abs{g(s)}^p \dd s,
	\end{aligned}
	\end{equation}
	which is the desired result.
\end{proof}

The following lemma characterizes the action of the filter when it is applied to polynomials.
\begin{lemma}\label{lem:FilterPoly} With the notation of Lemma \ref{lem:FilterJensen}, it holds for all $p \geq 0$
	\begin{equation}
		\int_0^t k(t-s)(t-s)^p \dd s \leq C \delta^p,
	\end{equation}
	where $C > 0$ is a positive constant independent of $\delta$.
\end{lemma}
\begin{proof} The change of variable $u = (t-s)/\delta$ yields
	\begin{equation}
		\int_0^t k(t-s)(t-s)^p \dd s = \delta^p \int_0^{t/\delta} u^p e^{-u} \dd u = \delta^p \gamma\left(p+1, \frac{t}{\delta}\right),
	\end{equation}
	where $\gamma$ is the lower incomplete Gamma function, which is bounded by the complete Gamma function $\Gamma(p+1)$ independently of the second argument.
\end{proof}
We can now prove a rough estimate of the difference between the trajectories $X_t^\epl$ and $Z_t^\epl$ when they are at stationarity.

@@

\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Lemma \ref{lem:distanceZandX} hold. Then the matrices $\mathcal M$ and $\widetilde{\mathcal M}_\epl$ defined in \eqref{eq:CalM} satisfy
	\begin{equation}
	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 \leq C\left(\epl + \delta^{1/2}\right),
	\end{equation}
	for a constant $C > 0$ independent of $\epl$ and $\delta$.
\end{lemma}
\begin{proof} Applying Jensen's and Cauchy--Schwarz inequalities we have
	\begin{equation}
	\begin{aligned}
	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 &\leq \E^{\rho^\epl} \norm{\left(V'(Z^\epl) - V'(X^\epl)\right) \otimes V'(X^\epl)}_2 \\
	&\leq \left(\E^{\rho^\epl}\norm{V'(Z^\epl) - V'(X^\epl)}_2^2\right)^{1/2} \left(\E^{\rho^\epl} \norm{V'(X^\epl)}_2^{2}\right)^{1/2}.
	\end{aligned}
	\end{equation}
	The Lipschitz condition on $V'$ together with the boundedness of the moments of $X^\epl$ and Lemma \ref{lem:distanceZandX} yield for a constant $C > 0$
	\begin{equation}
	\begin{aligned}
	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 &\leq C\left(\E^{\rho^\epl}\abs{Z^\epl - X^\epl}^{2}\right)^{1/2} \leq C \left(\epl + \delta^{1/2} \right),
	\end{aligned}
	\end{equation}
	which is the desired result.
\end{proof}

The final result presented in this section is a sharper quantification of the difference between $X^\epl_t$ and $Z^\epl_t$ than Lemma \ref{lem:distanceZandX}. In particular, denoting $Y_t^\epl \defeq X_t^\epl/\epl$, we will make use of the decomposition
\cite[Formula 5.8]{PaS07}
\begin{equation}\label{eq:App_DiffXtXs}
\begin{aligned}
	X_t^\epl - X_s^\epl &= -\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r\\
	&\quad +\sqrt{2\sigma} \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r - \epl(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)),
\end{aligned}
\end{equation}
which is obtained applying the Itô formula to $\Phi$, the solution of the cell problem \eqref{eq:CellProblem}.

@@

	where $\Phi$ is the solution of the cell problem \eqref{eq:CellProblem}, $W_s$ is the Brownian motion appearing in \eqref{eq:SDE_MS} and $Y_t^\epl = X_t^\epl / \epl$. Moreover, the remainder $R(\epl,\delta)$ satisfies for every $p > 0$ the estimate

@@

	\left( \E^{\rho_\epl} \left| R(\epl,\delta) \right|^p \right)^{1/p} \le C \left( \delta + \epl^2 + \epl \delta^{1/2} \right),

@@

	where $C$ is independent of $\epl$ and $\delta$.

@@

	in law, where the remainder $R_1^\epl$ satisfies 

@@

	I_1^\epl(t) &= -(A \cdot V'(X_t^\epl)) \int_0^t k(t-s) (t-s)\dd s + \int_0^t k(t-s)R^\epl(t-s) \dd s\\

@@

		Q_t \defeq \int_0^t \left(1 + \Phi'(Y_r^\epl)\right) \dd W_r,

@@

		I_2^\epl(t) = \sqrt{2\sigma} Q_t \int_0^t k(t-s)(Q_t - Q_s) \dd s.

@@

	An application of the Itô formula to $u(s, Q_s)$ where $u(s, x) = k(t-s)x$ yields

@@

		I_2^\epl(t) &= \sqrt{2\sigma} \left(Q_t\int_0^t k(t-s) \dd s - Q_t + \delta \int_0^t k(t-s)\left(1 + \Phi'(Y_s^\epl)\right) \dd W_s\right)\\
		  			&= \delta \beta_t^\epl - \sqrt{2\sigma} e^{-t/\delta} Q_t \eqdef \delta \beta_t^\epl - R_2^\epl(t).

@@

		\left(\E\abs{Q_t}^p\right)^2 \leq \E\abs{Q_t}^{2p} \leq Ct^{p-1}\int_0^t \E \abs{1 + \Phi'(Y_r^\epl)}^{2p} \dd r \leq C t

@@

		\E\abs{R_2^\epl(t)}^p \leq C \sqrt{t}e^{-pt/\delta}.

@@

@@

\corr{
\begin{remark} Let us remark that one can show for all $p \geq 1$ and a constant $C > 0$ independent of $\delta$
	\begin{equation}
		\left(\E\abs{\beta_t^\epl}^p \right)^{1/p} \leq C \delta^{-1/2}.
	\end{equation}
	Therefore, the estimate presented in Lemma \ref{lem:zeta} is consistent with the rough estimate of Lemma \ref{lem:distanceZandX}, and the term highlighted in the statement of Lemma \ref{lem:zeta} is indeed the dominating term in terms of powers of $\delta$.
\end{remark}
}

@@

\begin{proof}[Proof of Theorem \ref{thm:mainTheorem_zeta}]
	Let us introduce the notation
	\begin{equation}
		\mathcal A^\epl(\delta) = \frac1\delta \widetilde{\mathcal M}_\epl^{-1} \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)],
	\end{equation}
	where
	\begin{equation}
		\widetilde{\mathcal M}_\epl = \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ].
	\end{equation}
	Then following the proof of Theorem \ref{thm:mainTheorem} we only need to show that if $\delta = \epl^\zeta$ with $\zeta \in (0,1)$ we have
	\begin{equation}
		\lim_{\epl \to 0} \mathcal A^\epl(\delta) = A, \quad \text{in law}.
	\end{equation}
	Using Lemma \ref{lem:zeta} and geometric ergodicity (Lemma \ref{lem:ergodicity}), we have the following equality in law
	\begin{equation}
	\begin{aligned}
		\mathcal A^\epl(\delta) &= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E [(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl)] \\
		&= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E \left[ \left( \sqrt{2\Sigma}\delta \int_0^t k(t-s) \dd B_s + R(\epl,\delta) \right)^2 V''(Z_t^\epl) \right] \\
		&\eqdef \widetilde{\mathcal M}_\epl^{-1} \lim_{t \to \infty} \left( J_1^\epl(t) + J_2^\epl(t) + J_3^\epl(t) \right),
	\end{aligned}
	\end{equation}
	where
	\begin{equation}
	\begin{aligned}
		J_1^\epl(t) &= 2\Sigma\delta \E \left[ \left( \int_0^t k(t-s) \dd B_s \right)^2 V''(Z_t^\epl) \right], \\
		J_2^\epl(t) &= 2\sqrt{2\Sigma} \E \left[ \left( \int_0^t k(t-s) \dd B_s \right) R(\epl,\delta) V''(Z_t^\epl) \right], \\
		J_3^\epl(t) &= \frac1\delta \E\left[ R(\epl,\delta)^2 V''(Z_t^\epl) \right].
	\end{aligned}
	\end{equation}
	Let us consider the three terms separately. First, since the Brownian motion $B_s$ is independent of the process $Z_t^\epl$, applying Itô isometry we get
	\begin{equation}
	J_1^\epl(t) = 2\Sigma\delta \left( \int_0^t k(t-s)^2 \dd s \right) \E [V''(Z_t^\epl)] = \Sigma \E [V''(Z_t^\epl)],
	\end{equation}
	and, by Lemma \ref{lem:distanceZandX} and weak convergence of the invariant measure, we obtain
	\begin{equation}
	\lim_{\epl \to 0} \lim_{t \to \infty} J_1^\epl(t) = \Sigma \lim_{\epl \to 0} \E^{\rho^\epl} [V''(Z^\epl)] = \Sigma \E^{\rho^0} [V''(X)].
	\end{equation}
	Moreover, due to \eqref{eq:remainder_zeta}, we have the following bounds for $J_2^\epl(t)$ and $J_3^\epl(t)$
	\begin{equation}
	\begin{aligned}
		\abs{J_2^\epl(t)} &\le C \left( \delta^{1/2} + \epl^\iota \delta^{-1/2} + \epl \right), \\
		\abs{J_3^\epl(t)} &\le C \left( \delta + \epl^{2\iota} \delta^{-1} + \epl^2 \right).
	\end{aligned}
	\end{equation}
	Furthermore, by Lemma \ref{lem:distanceMandTildeM} and weak convergence of the invariant measure, we have
	\begin{equation}
		\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl^{-1} = \E^{\rho^0} [V'(X) \otimes V'(X) ] \eqdef \mathcal M_0.
	\end{equation}
	Therefore
	\begin{equation}
		\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ]^{-1} \E^{\rho^0} [V''(X)],
	\end{equation}
	and, finally, an integration by parts yields
	\begin{equation}
		\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ]^{-1} \frac1\Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ] A = A,
	\end{equation}
	which implies the desired result.
\end{proof}

@@

\begin{proof}[Proof of Theorem \ref{thm:mainTheoremTilde}] We first consider the difference between the two estimators $\widetilde A^\epl_k(T)$ and $\widehat A^\epl_k(T)$. In particular, the ergodic theorem and an algebraic equality imply
	\begin{equation}
	\begin{aligned}
	\lim_{T \to \infty} \left(\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)\right) &= \left(\mathcal M_\epl^{-1} - \widetilde{\mathcal M}_\epl^{-1}\right) \lim_{T \to \infty}\widetilde h \\
	&= \mathcal M_\epl^{-1}\left(\mathcal M_\epl - \widetilde{\mathcal M}_\epl\right)  \widetilde{\mathcal M}_\epl^{-1} \lim_{T \to \infty} \widetilde h\\
	&= \mathcal M_\epl^{-1}\left(\mathcal M_\epl - \widetilde{\mathcal M}_\epl\right)\lim_{T \to \infty} \widehat A^\epl_k(T),
	\end{aligned}
	\end{equation}
	almost surely. Therefore, due to Assumption \ref{as:regularity} which allows controlling the norm of $\mathcal M_\epl^{-1}$ and due to Lemma \ref{lem:distanceMandTildeM} we have for a constant $C > 0$
	\begin{equation}\label{eq:DistATildeAHat}
	\lim_{T \to \infty} \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 \leq C \left(\epl + \delta^{1/2} \right).
	\end{equation}
	Let us remark that $\widehat A^\epl_k(T)$ has a bounded norm for $\epl$ sufficiently small due to Theorem \ref{thm:mainTheorem}. Now, the triangle inequality yields
	\begin{equation}
	\norm{\widetilde A^\epl_k(T) - A}_2 \leq \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 + \norm{\widehat A^\epl_k(T) - A}_2.
	\end{equation}
	Therefore, due to Theorem \ref{thm:mainTheorem_zeta}, the inequality \eqref{eq:DistATildeAHat} and since $\delta \to 0$ for $\epl \to 0$, the desired result holds.
\end{proof}

>>>>

\corr{ CASE $\delta = \epl^\zeta$ (PROOF IN APPENDIX \ref{ap:zeta}).
\begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:convMeasure} hold, let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and let $\delta = \epl^\zeta$ with $\zeta \in (0,2)$. If $\widetilde M$ is invertible, then
		\begin{equation}
		\lim_{\epl \to 0} \lim_{T \to \infty} \widehat A_k^\epl(T) = A, \quad \text{in law},
		\end{equation}
		where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_MS}.
\end{theorem}}

@@

\begin{lemma}\label{lem:FilterJensen} Let $\delta > 0$ and $k(r)$ be defined as
	\begin{equation}
		k(r) = \frac1\delta e^{-r/\delta}.
	\end{equation}
	Then, for any $t > 0$, $p \geq 0$ and any function $g\in \mathcal C^0([0, t])$ it holds 
	\begin{equation}
		\abs{\int_0^t k(t-s) g(s) \dd s}^p \leq (1 - e^{-t/\delta})^{p-1}\int_0^t k(t-s) \abs{g(s)}^p \dd s.
	\end{equation}
	Moreover, if $p \geq 1$ and since $0 < (1-e^{-t/\delta}) < 1$ for all $t > 0$, it holds
	\begin{equation}
		\abs{\int_0^t k(t-s) g(s) \dd s}^p \leq \int_0^t k(t-s) \abs{g(s)}^p \dd s.
	\end{equation}
\end{lemma}
\begin{proof} Let us first note that
	\begin{equation}
		\int_0^t k(t-s) \dd s = 1 - e^{-t/\delta}.
	\end{equation}
	Therefore, the measure $\kappa_t(\d s)$ on $[0, t]$ defined as
	\begin{equation}
		\kappa_t(\d s) \defeq \frac{k(t-s)}{1 - e^{-t/\delta}} \dd s,
	\end{equation}
	is a probability measure. An application of Jensen's inequality therefore yields
	\begin{equation}
	\begin{aligned}
		\abs{\int_0^t k(t-s) g(s) \dd s}^p &\leq (1 - e^{-t/\delta})^p \int_0^t \abs{g(s)}^p \kappa_t(\d s) \\
		&= (1 - e^{-t/\delta})^{p-1} \int_0^t k(t-s) \abs{g(s)}^p \dd s,
	\end{aligned}
	\end{equation}
	which is the desired result.
\end{proof}

The following lemma characterizes the action of the filter when it is applied to polynomials.
\begin{lemma}\label{lem:FilterPoly} With the notation of Lemma \ref{lem:FilterJensen}, it holds for all $p \geq 0$
	\begin{equation}
		\int_0^t k(t-s)(t-s)^p \dd s \leq C \delta^p,
	\end{equation}
	where $C > 0$ is a positive constant independent of $\delta$.
\end{lemma}
\begin{proof} The change of variable $u = (t-s)/\delta$ yields
	\begin{equation}
		\int_0^t k(t-s)(t-s)^p \dd s = \delta^p \int_0^{t/\delta} u^p e^{-u} \dd u = \delta^p \gamma\left(p+1, \frac{t}{\delta}\right),
	\end{equation}
	where $\gamma$ is the lower incomplete Gamma function, which is bounded by the complete Gamma function $\Gamma(p+1)$ independently of the second argument.
\end{proof}

@@

The following result is a quantification of the difference between $X^\epl_t$ and $Z^\epl_t$. In particular, denoting $Y_t^\epl \defeq X_t^\epl/\epl$, we will make use of the decomposition
\cite[Formula 5.8]{PaS07}
\begin{equation}\label{eq:App_DiffXtXs}
\begin{aligned}
	X_t^\epl - X_s^\epl &= -\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r\\
	&\quad +\sqrt{2\sigma} \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r - \epl(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)),
\end{aligned}
\end{equation}
which is obtained applying the Itô formula to $\Phi$, the solution of the cell problem \eqref{eq:CellProblem}.

@@

	where $\Phi$ is the solution of the cell problem \eqref{eq:CellProblem}, $W_s$ is the Brownian motion appearing in \eqref{eq:SDE_MS} and $Y_t^\epl = X_t^\epl / \epl$. Moreover, $\beta_t^\epl$ and the remainder $R(\epl,\delta)$ satisfy for every $p > 0$ the estimates
	\begin{equation} \label{eq:beta}
	\left( \E^{\phi^\epl} \abs{\beta_t^\epl}^p \right)^{1/p} \leq C \delta^{-1},
	and

@@

	\left( \E^{\phi^\epl} \left| R(\epl,\delta) \right|^p \right)^{1/p} \le C \left( \delta + \epl \right),

@@

	where $C$ is independent of $\epl$ and $\delta$ and $\phi^\epl$ is the density of the invariant measure of $X^\epl$.

@@

	where the remainder $R_1^\epl$ satisfies 

@@

	I_1^\epl(t) &= -(A \cdot V'(X_t^\epl)) \int_0^t k(t-s) (t-s)\dd s + \int_0^t k(t-s)R_1^\epl(t-s) \dd s\\

@@

		Q_t^\epl \defeq \int_0^t \left(1 + \Phi'(Y_r^\epl)\right) \dd W_r,

@@

		I_2^\epl(t) = \sqrt{2\sigma} \int_0^t k(t-s)(Q_t^\epl - Q_s^\epl) \dd s.

@@

	An application of the Itô formula to $u(s, Q_s^\epl)$ where $u(s, x) = k(t-s)x$ yields

@@

		I_2^\epl(t) &= \sqrt{2\sigma} \left(Q_t^\epl\int_0^t k(t-s) \dd s - Q_t^\epl + \delta \int_0^t k(t-s)\left(1 + \Phi'(Y_s^\epl)\right) \dd W_s\right)\\
		  			&= \delta \beta_t^\epl - \sqrt{2\sigma} e^{-t/\delta} Q_t^\epl \eqdef \delta \beta_t^\epl - R_2^\epl(t).

@@

		\left(\E\abs{Q_t^\epl}^p\right)^2 \leq \E\abs{Q_t^\epl}^{2p} \leq Ct^{p-1}\int_0^t \E \abs{1 + \Phi'(Y_r^\epl)}^{2p} \dd r \leq C t^p

@@

		\left( \E^{\phi^\epl}\abs{R_2^\epl(t)}^p \right)^{1/p} \leq C \sqrt{t} e^{-t/\delta}.

@@

	Moreover, applying the Itô isometry and due to the boundedness of $\Phi'$, we get
	\E^{\phi^\epl} \abs{\beta_t^\epl}^2 \le C \int_0^t k^2(t-s) \dd s \leq C \delta^{-1},
	which proves \eqref{eq:beta}.

@@

Corollary \ref{cor:distanceZandX} is a direct consequence of Lemma \ref{lem:zeta} and provides a rough estimate of the difference between the trajectories $X_t^\epl$ and $Z_t^\epl$ when they are at stationarity.

\begin{corollary} \label{cor:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$. Then, if $\delta \leq 1$, it holds for any $p \geq 1$
	\begin{equation}
	\left(\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p\right)^{1/p} \leq C\left(\epl + \delta^{1/2}\right),
	\end{equation}
	for a constant $C > 0$ independent of $\epl$ and $\delta$.
\end{corollary}
\begin{proof}
	Let $p \geq 1$, then due to Lemma \ref{lem:zeta} there exists a constant $C > 0$ depending only on $p$ such that
	\begin{equation}
	\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p \leq C\left(\epl^p + \delta^{p/2}\right).
	\end{equation}
	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$. In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $C$ depending on the initial condition and $p$  
	\begin{equation}
	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p + Ce^{-\lambda t},
	\end{equation}
	which, for $t$ sufficiently big, yields the desired result.
\end{proof}

\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Lemma \ref{lem:distanceZandX} hold. Then the matrices $\mathcal M$ and $\widetilde{\mathcal M}_\epl$ defined in \eqref{eq:CalM} satisfy
	\begin{equation}
	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 \leq C\left(\epl + \delta^{1/2}\right),
	\end{equation}
	for a constant $C > 0$ independent of $\epl$ and $\delta$.
\end{lemma}
\begin{proof} Applying Jensen's and Cauchy--Schwarz inequalities we have
	\begin{equation}
	\begin{aligned}
	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 &\leq \E^{\rho^\epl} \norm{\left(V'(Z^\epl) - V'(X^\epl)\right) \otimes V'(X^\epl)}_2 \\
	&\leq \left(\E^{\rho^\epl}\norm{V'(Z^\epl) - V'(X^\epl)}_2^2\right)^{1/2} \left(\E^{\rho^\epl} \norm{V'(X^\epl)}_2^{2}\right)^{1/2}.
	\end{aligned}
	\end{equation}
	The Lipschitz condition on $V'$ together with the boundedness of the moments of $X^\epl$ and Corollary \ref{cor:distanceZandX} yield for a constant $C > 0$
	\begin{equation}
	\begin{aligned}
	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 &\leq C\left(\E^{\rho^\epl}\abs{Z^\epl - X^\epl}^{2}\right)^{1/2} \leq C \left(\epl + \delta^{1/2} \right),
	\end{aligned}
	\end{equation}
	which is the desired result.
\end{proof}

@@

\begin{lemma} \label{lem:quartet}
	Let $\eta^\epl$ be the invariant measure of the quartet $(X^\epl, Y^\epl, Z^\epl, \beta^\epl)$. Then it holds
	\begin{equation}
	\delta \E^{\eta^\epl} \left[ (\beta^\epl)^2 V''(Z^\epl) \right] = \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta),
	\end{equation}
	where the remainder $\widetilde R(\epl,\delta)$ satisfies
	\begin{equation} \label{eq:quartet_remainder}
	\left( \E^{\eta^\epl} \left| \widetilde R(\epl,\delta) \right|^p \right)^{1/p} \le C \left( \delta^{3/2} + \delta \epl \right).
	\end{equation}
\end{lemma}
\begin{proof}

\begin{lemma} \label{lem:quartet_convergence}
	It holds
	\begin{equation}
	\lim_{\epl \to 0} \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] = \Sigma \E^{\phi^0} [V''(X)].
	\end{equation}
\end{lemma}
\begin{proof}

\begin{proof}[Proof of Theorem \ref{thm:mainTheorem_zeta}]
	Let us introduce the notation
	\begin{equation}
		\mathcal A^\epl(\delta) = \frac1\delta \widetilde{\mathcal M}_\epl^{-1} \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)],
	\end{equation}
	where
	\begin{equation}
		\widetilde{\mathcal M}_\epl = \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ].
	\end{equation}
	Then following the proof of Theorem \ref{thm:mainTheorem} we only need to show that if $\delta = \epl^\zeta$ with \corr{$\zeta \in (0,2)$} we have
	\begin{equation}
		\lim_{\epl \to 0} \mathcal A^\epl(\delta) = A, \quad \text{in law}.
	\end{equation}
	Using Lemma \ref{lem:zeta} and geometric ergodicity (Lemma \ref{lem:ergodicity}), we have the following equality
	\begin{equation}
	\begin{aligned}
		\mathcal A^\epl(\delta) &= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E [(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl)] \\
		&= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E \left[ \left( \delta \beta_t^\epl + R(\epl,\delta) \right)^2 V''(Z_t^\epl) \right] \\
		&\eqdef \widetilde{\mathcal M}_\epl^{-1} \lim_{t \to \infty} \left( J_1^\epl(t) + J_2^\epl(t) + J_3^\epl(t) \right),
	\end{aligned}
	\end{equation}
	where and $\E$ denotes the expectation with respect to the Wiener measure and
	\begin{equation}
	\begin{aligned}
		J_1^\epl(t) &= \delta \E \left[ (\beta_t^\epl)^2 V''(Z_t^\epl) \right], \\
		J_2^\epl(t) &= 2 \E \left[ \beta_t^\epl R(\epl,\delta) V''(Z_t^\epl) \right], \\
		J_3^\epl(t) &= \frac1\delta \E\left[ R(\epl,\delta)^2 V''(Z_t^\epl) \right].
	\end{aligned}
	\end{equation}
	Let us consider the three terms separately. First, by geometric ergodicity and applying Lemma \ref{lem:quartet}, we get
	\begin{equation}
	\lim_{t \to \infty} J_1^\epl(t) = \delta \E^{\eta^\epl} \left[ (\beta^\epl)^2 V''(Z^\epl) \right] = \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta),
	\end{equation}
	and, by Lemma \ref{lem:quartet_convergence} and due to \eqref{eq:quartet_remainder}, we obtain
	\begin{equation}
	\lim_{\epl \to 0} \lim_{t \to \infty} J_1^\epl(t) = \Sigma \E^{\rho^0} [V''(X)].
	\end{equation}
	Moreover, due to \eqref{eq:beta} and \eqref{eq:remainder_zeta}, we have the following bounds for $J_2^\epl(t)$ and $J_3^\epl(t)$
	\begin{equation}
	\begin{aligned}
		\abs{J_2^\epl(t)} &\le C \left( \delta^{1/2} + \epl \delta^{-1/2} \right), \\
		\abs{J_3^\epl(t)} &\le C \left( \delta + \epl^2 \delta^{-1} \right).
	\end{aligned}
	\end{equation}
	Furthermore, by Lemma \ref{lem:distanceMandTildeM} and weak convergence of the invariant measure, we have
	\begin{equation}
		\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl^{-1} = \E^{\rho^0} [V'(X) \otimes V'(X) ] \eqdef \mathcal M_0.
	\end{equation}
	Therefore
	\begin{equation}
		\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ]^{-1} \E^{\rho^0} [V''(X)],
	\end{equation}
	and, finally, an integration by parts yields
	\begin{equation}
		\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ]^{-1} \frac1\Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ] A = A,
	\end{equation}
	which implies the desired result.
\end{proof}

@@

\begin{proof}[Proof of Theorem \ref{thm:mainTheoremTilde}] We first consider the difference between the two estimators $\widetilde A^\epl_k(T)$ and $\widehat A^\epl_k(T)$. In particular, the ergodic theorem and an algebraic equality imply
	\begin{equation}
	\begin{aligned}
	\lim_{T \to \infty} \left(\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)\right) &= \left(\mathcal M_\epl^{-1} - \widetilde{\mathcal M}_\epl^{-1}\right) \lim_{T \to \infty}\widetilde h \\
	&= \mathcal M_\epl^{-1}\left(\mathcal M_\epl - \widetilde{\mathcal M}_\epl\right)  \widetilde{\mathcal M}_\epl^{-1} \lim_{T \to \infty} \widetilde h\\
	&= \mathcal M_\epl^{-1}\left(\mathcal M_\epl - \widetilde{\mathcal M}_\epl\right)\lim_{T \to \infty} \widehat A^\epl_k(T),
	\end{aligned}
	\end{equation}
	almost surely, where $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ are defined in \eqref{eq:CalM}. Therefore, due to Assumption \ref{as:regularity} which allows controlling the norm of $\mathcal M_\epl^{-1}$ and due to Lemma \ref{lem:distanceMandTildeM} we have for a constant $C > 0$
	\begin{equation}\label{eq:DistATildeAHat}
	\lim_{T \to \infty} \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 \leq C \left(\epl + \delta^{1/2} \right).
	\end{equation}
	Let us remark that $\widehat A^\epl_k(T)$ has a bounded norm for $\epl$ sufficiently small due to Theorem \ref{thm:mainTheorem}. Now, the triangle inequality yields
	\begin{equation}
	\norm{\widetilde A^\epl_k(T) - A}_2 \leq \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 + \norm{\widehat A^\epl_k(T) - A}_2.
	\end{equation}
	Therefore, due to Theorem \ref{thm:mainTheorem_zeta}, the inequality \eqref{eq:DistATildeAHat} and since $\delta \to 0$ for $\epl \to 0$, the desired result holds.
\end{proof}
